Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-26 DQC3.tex
Keep adding comments on "The Concept of Contextuality and its..."

>>>>

\yutsung{Does the sentences in this paragraph contradict to each
other? Besides, are we talking about CQT or DQT here? The paragraph
only make sense if we can simultaneously measuring commuting observables
in CQT so that we could implement an observable in many different
measurement processes. For example, in CQT, we could implement $J_{z}$
in two different measurement processes: measuring $J_{z}$ directly,
or measuring $J_{z}^{2}$ and then $J_{z}$. These two processes are
the same because $J_{z}$ and $J_{z}^{2}$ are commuting, and can
measure simultaneously. However, these two processes are not the same
in DQT because the first always success, but the second one may produce
a zero-norm state in the middle. In general, observables cannot measure
simultaneously in DQT. Because the definition of contextuality is
based on simultaneously measurement in CQT, we must redefine the contextuality
in DQT to address this issue.

What does contextuality mean in CQT? Assume:
\begin{enumerate}
\item The quantum system were actually classical, i.e., we could assign
each observable~$\mathbf{O}$ a measurement result~$v\left(\mathbf{O}\right)$
before we do any measurement.
\end{enumerate}
Because whether measuring commuting observables of $\mathbf{O}$ or
not doesn't change the measurement result of $\mathbf{O}$, it is
nature to hope this property still hold if the quantum system were
actually classical. Therefore, we assume:
\begin{enumerate}[resume]
\item \label{enu:contextuality}The preassigned measurement result~$v\left(\mathbf{O}\right)$
of an observable~$\mathbf{O}$ is not changed if we measure the system
by any other observable commuting to $\mathbf{O}$. (page 207 in~\cite{peres1995quantum})
\end{enumerate}
Then, we have the premise of the Kochen-Specker theorem
\begin{enumerate}[resume]
\item \label{enu:premise}For a set of commuting projection operator $\proj{n}$,
if $\left\{ \ket{n}\right\} $ forms a basis, then $\sum_{n}v\left(\proj{n}\right)=1$.
(page 196 in~\cite{peres1995quantum}).
\end{enumerate}
The Kochen-Specker theorem says Premise (\ref{enu:premise}) is impossible
to be satisfied, so that Assumption (\ref{enu:contextuality}) cannot
be true.

Schumacher and Westmoreland\cite{2010arXiv1010.5452S} uses Premise
(\ref{enu:premise}) as the definition of contextuality because it
seems impossible to discuss the commuting observables in their theory.
Our paper may do better and use Assumption (\ref{enu:contextuality})
as contextuality. However, it is not that surprising if Assumption
(\ref{enu:contextuality}) is false because commuting observables
cannot be measured simultaneously in DQT anyway. }
